\Title

### 2020-02-26 manuscript/manuscript.tex
Replace airborne for ground on fig caption
Include parameter tables on manuscript

\documentclass[twocolumn]{article}
\usepackage[left=0.7in,right=0.7in,top=1in,bottom=1in]{geometry}
\setlength{\columnsep}{2\columnsep}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[round]{natbib}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\usepackage{fancyhdr}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{figs/ground-survey.pdf}
    \caption{
        Synthetic ground survey.
        (a)~Location of observation points. Altitude given in meters above the
            zero height plane.
        (b)~Vertical component of gravity acceleration generated by the
            synthetic model plus Gaussian noise on the airborne survey
            observation points.
    }
    \label{fig:synthetic-ground-survey}
\end{figure}

@@

>>>>

\documentclass[twocolumn]{article}
\usepackage[left=0.7in,right=0.7in,top=1in,bottom=1in]{geometry}
\setlength{\columnsep}{2\columnsep}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[round]{natbib}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\usepackage{fancyhdr}
\usepackage{multirow}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{figs/ground-survey.pdf}
    \caption{
        Synthetic ground survey.
        (a)~Location of observation points. Altitude given in meters above the
            zero height plane.
        (b)~Vertical component of gravity acceleration generated by the
            synthetic model plus Gaussian noise on the ground survey
            observation points.
    }
    \label{fig:synthetic-ground-survey}
\end{figure}

@@

\appendix

\section{Source distributions parameters}

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic ground survey. Depths and spacings are given in km.
    }
    \label{tab:parameters-ground-survey}
    \input{parameters_ground_survey.tex}
\end{table*}

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic airborne survey. Depths and spacings are given in km.
    }
    \label{tab:parameters-airborne-survey}
    \input{parameters_airborne_survey.tex}
\end{table*}
